\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-08 cfhtlens.tex
rest of PS's comments

\subsection{On the application to CMB lensing}
\citet{kitching/etal:2016} discuss how corrections to the Limber and flat-sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that the cross-correlation of CMB lensing and galaxy lensing should include a pre-factor $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4$.   We have verified that this term would have negligible impact on current measurements, given the relatively low signal to noise ratio.  For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$.  The size of the pre-factor, averaged over this range, is of the order of 0.01\%. In comparison, the size of the statistical error bars are of the order 25-35\% with additional uncertainty due to photometric redshifts (10-15\%) and intrinsic galaxy alignments (10-15\%). The pre-factor reaches 1\% only for $\ell < 7$, which may become relevant for very large upcoming surveys but is negligible for current surveys.

>>>>

\subsection{On the application to CMB lensing}
\citet{kitching/etal:2016} discuss how corrections to the Limber and flat-sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that the cross-correlation of CMB lensing and galaxy lensing should include a pre-factor $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4 = 1-{1\over 2\ell^2}+{\cal O}(\ell^{-3})$.   We have verified that this term would have negligible impact on current measurements, given the relatively low signal to noise ratio.  For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$.  The size of the pre-factor, averaged over this range, is of the order of 0.01\%. In comparison, the size of the statistical error bars are of the order 25-35\% with additional uncertainty due to photometric redshifts (10-15\%) and intrinsic galaxy alignments (10-15\%). The pre-factor reaches 1\% only for $\ell < 7$, which may become relevant for very large upcoming surveys but is negligible for current surveys.

### 2016-12-08 conclusion.tex
Added names (TBC; Patrick/Peter)
Added Lance to the thnx
rest of PS's comments

In this comment we have highlighted a number of shortcomings in the analysis presented in \cite{kitching/etal:2016}.  We argue that the flat sky and Limber approximations that can be used in cosmic shear analyses are not able to explain away the tension between current weak lensing and Planck results, in contrast to the message that \cite{kitching/etal:2016} convey.  Our critique should not, however, detract from the important core message of their paper, that future surveys will need to consider these approximations and optimise their statistical analyses accordingly.  For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{schneider/etal:2010} renders the cosmic shear measurement completely insensitive to the low-$\ell$ scales where these approximations become important.

@@

>>>>

In this comment we have highlighted a number of shortcomings in the analysis presented in \cite{kitching/etal:2016}.  We argue that the flat-sky and Limber approximations that can be used in cosmic shear analyses are not able to explain away the tension between current weak lensing and Planck results, in contrast to the message that \cite{kitching/etal:2016} convey.  Our critique should not, however, detract from the important core message of their paper, that future surveys will need to consider these approximations and optimise their statistical analyses accordingly.  For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{schneider/etal:2010} renders the cosmic shear measurement completely insensitive to the low-$\ell$ scales where these approximations become important.

@@

\section{Acknowledgements}
We thank Sarah Bridle, Ami Choi, Tommaso Giannantonio, Donnacha Kirk, Lance Miller, Benjamin Joachimi and Adam Amara for useful discussions during the collection of these comments.
